\documentclass{article}
\usepackage{amsmath, amssymb, amsfonts, amsthm}
\usepackage{cancel}
\usepackage[output-complex-root=j]{siunitx}
\usepackage[american, nooldvoltagedirection]{circuitikz}
\usepackage{bm}
\usepackage{listings}
\usepackage{graphicx}
\usepackage{fullpage}
\usepackage{hyperref}

\renewcommand{\thesection}{\arabic{section}}
\renewcommand{\thesubsection}{\thesection.\alph{subsection}}
\renewcommand{\thesubsubsection}{\thesubsection.\roman{subsubsection}}
\renewcommand{\labelenumi}{\alph{enumi}.}

\newtheorem{genthm}{Theorem}

\newcommand{\unit}[1]{\bm{\hat{#1}}}
\newcommand{\iprod}[2]{\left\langle #1, #2 \right\rangle}
\newcommand{\tpose}[1]{\left[#1\right]^{\! \top} \!\!}
\newcommand{\diff}[1]{\frac{d}{d #1}}

\lstset{
    language=Python,
    tabsize=4,
    basicstyle=\ttfamily,
    numbers=left,
    numberstyle=\ttfamily,
    keywordstyle=\color{blue},
    frame=single
}

\title{CS70 HW00}
\author{Bryan Ngo}
\date{2020-08-26}

\begin{document}

\maketitle

I worked on this homework by myself.

\section{Administrivia}

\subsection{}

\url{https://www.eecs70.org/}

\subsection{}

\subsubsection{}

\begin{tabular}{||c|c||}
    \hline
    \textbf{With Homework} & \\
    \hline
    Discussion Attendance & \(5\%\) \\
    Vitamin & \(5\%\) \\
    Homework & \(20\%\) \\
    Midterm & \(30\%\) \\
    Final & \(40\%\) \\
    \hline
\end{tabular} \\
\begin{tabular}{||c|c||}
    \hline
    \textbf{Without Homework} & \\
    \hline
    Discussion Attendance & \(6.25\%\) \\
    Vitamin & \(6.25\%\) \\
    Midterm & \(37.5\%\) \\
    Final & \(50\%\) \\
    \hline
\end{tabular}

\subsubsection{}

You must attend \(\frac{14}{27}\) for full credit.

\subsubsection{}

Yes, but it will be counted under the section you originally signed up for.

\subsubsection{}

Vitamins are due Fridays at 20:00 PT.

\section{}

\begin{enumerate}
    \item \textbf{Yes}, Alice and Bob worked \emph{together} on a solution rather than individually, despite having acknowledged each other's work.
    \item \textbf{No}, Carol used Dan's description of his approach in order to come up with a solution herself, while also crediting Dan.
    \item \textbf{No}, Erin was assisted by the online resource and simply adopted their approach rather than copying verbatim, while also citing the resource.
    \item \textbf{Yes}, Frank copied Grace's solution verbatim.
    \item \textbf{Yes}, Irene was in possession of the entirety of Heidi's solutions.
    \item \textbf{Yes}, Joe is in possession of active homework solutions.
\end{enumerate}

\section{Use of Piazza}

\begin{enumerate}
    \item @11
    \item Since XYZ is complicated, it'll probably take more than 5 minutes to answer, so it should be relegated to office hours.
    \item Weekly posts are posted on Sundays, and are required reading.
\end{enumerate}

\section{Timezone}

The magic word is "soda pies".

\section{Academic Integrity}

I pledge to uphold the university's honor code: to act with honesty, integrity, and respect for others, including their work.
By signing, I ensure that all written homework I submit will be in my own words, that I will acknowledge any collaboration or help received, and that I will neither give nor receive help on any examinations.

\begin{flushright}
    \textit{Bryan Ngo}
\end{flushright}

\end{document}
